External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-08 CVPR2017_Review_Unified.tex
ad

In the last decade, researchers proposed many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for real image denoising problem. In \cite{fullyblind}, Portilla proposed to use scale mixture of Gaussian to estimate the noise covariance matrix and latent clean images in wavelet domain. The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}. Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Later, Lebrun el al. proposed a multiscale denoising algorithm called 'Noise Clinic' \cite{noiseclinic,ncwebsite}. This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via Low-Rank Mixture of Gaussians. Though these methods are , these methods In this paper, we proposed a noval denoising method achieving much better performance than previous real denoising methods.

@@

\subsection{External Patch Group Prior Learning}

@@

In this work, each local patch extracted from RGB images is of size $p\times p \times 3$. Then we search the $M$ most similar patches $\{\mathbf{x}_{m}\}_{m=1}^{M}$ around each local patch through Euclidean distance, in a local window of size $W\times W$. The $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ is a patch vector formed by combining the 3 patch vectors (of size $p^{2}\times 1$) in R, G, B channels. The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}\}, m=1,...,M$. Assume we have extracted $N$ PGs from a set of external natural images, and the $n$-th PG is defined as $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$. We employ the Gaussian Mixture Model (GMM) to learn the external patch group based NSS prior. In this model, the likelihood of the $n$-th PG $\{\mathbf{\overline{X}}_{n}\}$ can be calculated as
\vspace{-2mm}
\begin{equation}\label{equ1}\vspace{-2mm}
P(\mathbf{\overline{X}}_{n})  = \sum\nolimits_{k=1}^{K}\pi_{k}\prod\nolimits_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k}),
\end{equation}
where $K$ is the number of Gaussians and the parameters $\pi_{k}$, $\boldsymbol{\upmu}_{k}$, $\mathbf{\Sigma}_{k}$ are mixture weight, mean vector, and covariance matrix of the $k$-th Gaussian, respectively. By assuming that all the PGs are independently sampled, the overall objective log-likelihood function is
\vspace{-2mm}
\begin{equation}\label{equ2}\vspace{-2mm}
\begin{split}
\ln\mathcal{L}=\sum_{n=1}^{N} \ln(\sum_{k=1}^{K}\pi_{k}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})).
\end{split}
\end{equation} 
We maximize the above objective function via EM algorithm \cite{em} and finally obtain the GMM model with learned parameters. Similar to \cite{pgpd}, the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.

@@

\vspace{-2mm}
\subsubsection{Guided Internal Subspace Selection}
\vspace{-1mm}

@@

\vspace{-2mm}
\subsubsection{Guided Internal Orthogonal Dictionary Learning}
\vspace{-2mm}

>>>>

In the last decade, researchers proposed many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for real image denoising problem. In \cite{fullyblind}, Portilla proposed to use scale mixture of Gaussians to estimate the noise covariance matrix and latent clean images in wavelet domain. The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}. Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Later, Lebrun el al. proposed a multiscale denoising algorithm called ``Noise Clinic" \cite{noiseclinic,ncwebsite}. This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians. However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explict distributions. Besides, the parametric estimation of the Gaussian or MoG distribution is time consumming.

@@

\subsection{Learn External Patch Group Prior}

@@

In this work, each local patch extracted from RGB images is of size $p\times p \times 3$. Then we search the $M$ most similar patches $\{\mathbf{x}_{m}\}_{m=1}^{M}$ around each local patch through Euclidean distance, in a local window of size $W\times W$. The $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ is a patch vector formed by combining the 3 patch vectors (of size $p^{2}\times 1$) in R, G, B channels. The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}\}, m=1,...,M$. Assume we have extracted $N$ PGs from a set of external natural images, and the $n$-th PG is defined as $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$. We employ the Gaussian Mixture Model (GMM) to learn the external patch group based NSS prior. The overall objective log-likelihood function of GMM is
\begin{equation}\label{equ2}
\begin{split}
\ln\mathcal{L}=\sum_{n=1}^{N} \ln(\sum_{k=1}^{K}\pi_{k}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})).
\end{split}
\end{equation}
The learning process is similar to the learning stage of the PGPD method \cite{pgpd}. Please refer to \cite{pgpd} for more details. After the learning stage, we finally obtain a GMM model with $K$ Gaussian components. The learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$. Similar to \cite{pgpd}, the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.

@@

\vspace{-2mm}
\subsubsection{Internal Subspace Selection}
\vspace{-1mm}

@@

\vspace{-2mm}
\subsubsection{Internal Orthogonal Dictionary Learning}
\vspace{-2mm}
